\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{makeidx}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{color}
\usepackage[all]{xy}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\long\def\remove#1{}
\newcommand{\dom}{\mbox{dom}}

\newcommand{\vp}{\varphi}


\newcommand{\coNP}{\mbox{coNP}}

\newcommand{\NP}{\mbox{NP}}
\newcommand{\DP}{\mbox {D}^P}

\newcommand{\LeKl}{\mbox{$\sqcup$ }}
\newcommand{\card}[1]{\mbox{\#}(#1)}

\newcommand{\sss}{\mbox{\bf S}}
\newcommand{\jjj}{\mbox{\bf J}}

\newcommand{\QR}[1]{\mbox{$\ \mid\!\!\!\frac{#1}{\
    \stackrel{\mbox{\scriptsize\it Q-Res}}{\ }\ }\ $}}
\newcommand{\QUR}[1]{\mbox{$\ \mid\!\!\!\frac{#1}{\
    \stackrel{\mbox{\scriptsize\it Q-Pos-Unit-Res}}{\ }\ }\ $}}
%\baselineskip 0.2in

\newcommand{\AK}{\mbox{${\cal{A}}_K$}}

\newcommand{\pbox}{\hbox to 6pt{\leaders\hrule width 6pt height 6pt\hfill}}

\newtheorem{definition}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{example}{Example}[section]
\newtheorem{remark}{Remark}[section]
\newenvironment{proof}{\parindent=0pt{\bf Proof: }}{
   \hspace*{\fill}\hbox to 6pt{\leaders\hrule width 6pt height 6pt\hfill}\par}


\pagestyle{plain}

\begin{document}


\begin{tabular}{l|l|l|l}
& $\equiv$ & $\equiv_V$ & $\models$\\ \hline
DHORN & PTIME & $\Sigma_2^P$, hardness is unknown & PTIME \\ \hline
HORN & PTIME & $\Sigma_2^P$-complete & NP-complete\\ \hline
CNF & $P^{NP[\text{log}\, n]}$-complete & $\Sigma_3^P$-complete & $\Sigma_2^P$-complete
\end{tabular}


\section{General Problems}

Configuration and Specification (Sets)\\ \ \\

{\bf Equivalence Configuration Problem}\\

Input: $C=\{\alpha_1,\cdots,\alpha_n\}$ and $\beta$

Query: Whether $\exists K\subseteq C: K\equiv \beta$\\

Let
$$\mbox{IMP}(C,\beta):=\{\alpha\mid \alpha\in C \mbox{ and }\beta\models \alpha\}$$
Then
$$\exists K\subseteq  C(K \text{ is satisfiable and } K\equiv \beta)\Longleftrightarrow\mbox{IMP}(C,\beta) \text{ is satisfiable and IMP}(C,\beta)\models \beta$$

So, equivalence problem is in P$^{\text{NP}[\text{log} n]}$ which is the class of problems solvable in polynomial time with $O(\text{log}n)$ queries to an NP oracle.\\

Next we show hardness. The problem SAT$^n_{\text{odd}}$ is complete for P$^{\text{NP}[\text{log} n]}$. Where SAT$^n_{\text{odd}}$ is the problem of determining whether the number of satisfiable formulas among $n$ given CNF formulas.

We shall construct a reduction from SAT$^n_{\text{odd}}$ to the equivalence configuration problem. 

Suppose $F_1,\cdots, F_n$ are 3CNF formulas such that they have pairwisely distinct variables. We assume $n$ is $2^k$. Otherwise we add some formulas like $p\wedge \neg p$. \\

We also assume each $F_i$ is not tautological (otherwise condider $F_i\wedge p_i$).\\ 

We assume $F_i$ is over variables $\vec{x}_i$. 



$$C_{ij}:=\{(f_i\wedge \neg f_j)\wedge \varphi_{ij}), 
((\neg f_i\wedge f_j)\wedge \varphi_{ij}), 
((f_i\wedge f_j)\wedge \varphi_{ij}),
((\neg f_i\wedge \neg f_j)\wedge \varphi_{ij})\}
$$

$$C_0:=C_{12}\cup C_{34}\cup\cdots\cup C_{(n-1)n}\cup \{f_1,\cdots, f_n\}$$


$$\begin{array}{ll}C_1:=&\{f_{12}=f_1\oplus f_2, \cdots, f_{(n-1)n}=f_{n-1}\oplus f_n\}\cup \\

&\{f_{1234}=f_{12}\oplus f_{34}, \cdots, f_{(n-3)(n-2)(n-1)n}=f_{(n-3)(n-2)}\oplus f_{(n-1)n}\}\cup \\

&\cdots\cdots \\

&\{f_{final}=f_{1\cdots2^{k-1}}\oplus f_{(2^{k-1}+1)\cdots n}\}
\end{array}
$$


$$C:=C_0\cup C_1$$

$$\beta:=C_1\cup \{f_1\rightarrow F_1, \cdots, f_n\rightarrow F_n\}\wedge f_{final}$$


\remove{

$$C_0=\{ f_1\rightarrow F_1,\cdots, f_n\rightarrow F_n \}$$

$$\varphi_{ij}=(f_i\rightarrow F_i)\wedge (f_j\rightarrow F_j)$$ 

$$\beta_{ij}:=((f_i\wedge \neg f_j)\wedge \varphi_{ij}) \vee 
((\neg f_i\wedge f_j)\wedge \varphi_{ij})\vee 
((f_i\wedge f_j)\wedge \varphi_{ij})\vee 
((\neg f_i\wedge \neg f_j)\wedge \varphi_{ij})
$$




$$\begin{array}{ll}C_1:=&\{f_{12}=f_1\oplus f_2, \cdots, f_{(n-1)n}=f_{n-1}\oplus f_n\}\cup \\

&\{f_{1234}=f_{12}\oplus f_{34}, \cdots, f_{(n-3)(n-2)(n-1)n}=f_{(n-3)(n-2)}\oplus f_{(n-1)n}\}\cup \\

&\cdots\cdots \\

&f_{final}=f_{1\cdots2^{k-1}}\oplus f_{(2^{k-1}+1)\cdots n}
\end{array}
$$

$$C=C_0\cup C_1\cup\{f_1,\cdots, f_n\}$$

$$\beta = \beta_{12}\wedge \cdots\wedge \beta_{(n-1)n}\wedge C_1\wedge f_{final}$$
}

\ \\

{\bf Retricted Equivalence Configuration}(R-equivalence)\\

Input: $C=\{\alpha_1,\cdots,\alpha_n\}$, $\beta$, and a set $V$ of variables

Query: Whether $\exists K\subseteq C: K\equiv^V \beta$\\ 



the problem of determining whether $F\equiv_V G$  is in $\Pi_2^P$ (for the complementary problem: we guess a clause $\gamma$ over $V$, check that $G\models \gamma$ but $F\not\models \gamma$, or $G\not\models\gamma$ but $F\models\gamma$). 

Thus, R-equivalence configuraton is $\Sigma_3^P$ (guess a $K\subseteq C$, check that it is satisfiable and $K\equiv_V \beta$.) \\


Next we show the hardness.

Consider $\Phi:=\exists \vec{x}\forall\vec{y}\exists \vec{z} \varphi$ where $\varphi$ is a CNF formula. \\

We assume w.l.o.g. that $\varphi$ contains a non-tautological clause over $\vec{z}$ (otherwise, we pick new varaiable $z'$ and consider $\exists\vec{x}\forall\vec{y}\exists\vec{z}\exists z'(\varphi\wedge z'$)).

By this assumption, $\forall\vec{x}\exists\vec{y}\exists\vec{z}\neg \varphi$ is true\\

We assume that each clause contains a positive occurrence of a variable from $\vec{y}\cup\vec{z}$. If otherwise pick a new variable $u$, and consider $\exists \vec{x}\forall\vec{y}\forall u\exists \vec{z}\varphi^u$, where $\varphi^u$ is obtained from $\varphi$ by adding $u$ to clauses containing no positive literal from $\vec{y}\cup\vec{z}$. Clearly, $\Phi$ and the resulting formula has the same truth.

By this assumption, $\forall\vec{x}\exists\vec{y}\exists\vec{z}\phi$ is true. (we will use this later).\\ 

$\varphi$ can be written as $(c'_1\vee c''_1)\wedge\cdots\wedge (c'_n\vee c''_n)$ in which $c'_i$ is over $\vec{x}$, while $c''_i$ is over $\vec{y}\cup\vec{z}$.

Pick new variables $w_1, \cdots, w_n,w$. Let 

Let $$\psi:= \left(\bigwedge_{i=1}^n (c'_i\rightarrow w_i)\right)\wedge 
\left(\bigwedge_{i=1}^n(\neg c'_i\wedge \neg c''_i\rightarrow \neg w_i)\right)$$

Let $$C_0:=\{\psi\wedge \neg c'_1\wedge  (c''_1\rightarrow w_1) , \cdots, \psi\wedge\neg c'_n\wedge (c''_n\rightarrow w_n)\}$$

$$C_1=\{c'_1, \cdots, c'_n, \}$$

$$C_2=\{x_1,\neg x_1\cdots, x_n,\neg x_n\}$$

$$C_3=\{(w\rightarrow (c'_1\vee c''_1)\wedge\cdots\wedge (c'_n\vee c''_n))\}$$

Now let $$C:=C_0\cup C_1\cup C_2\cup C_3\cup\{w\}$$

Let $\beta$ be $$ w_1\wedge\cdots\wedge w_n\wedge w$$

Let $V:=\vec{y}\cup\{w_1,\cdots,w_n,\}\cup\{w\}$\\


%Claim: Suppose $K\subseteq C$ satisfiable, $c_i\not \in K$ and $K\not\models c_i$, %then 
%$K\cup\{\neg c_i, \psi\wedge (c''_i\rightarrow w_i)\}$ is still satisfiable.


(Lemma: $F\models_V G$ iff for for any truth assignment $t$ on $V$, if it can be extended to a satisfying truth assignment for $F$, it can be extended to an satisfying truth assignment for $G$. 
) \\

We shall show $\Phi$ is true if and only if there is satisfiable $K\subseteq C$ s.t. $K\equiv_V \beta$\\



\color{red} From right to left:\color{black}

Given a such $K\equiv_V \beta$. 
Clearly, $K\cap C_0$ is non-empty.\\



It must be that $w\in K$. 
Let $t$ satisfy $K$. 
By our assumption we know $t\uparrow\vec{x}$ can be extended to $s$ which falsifies $\varphi$. Now we assign truth values to $w_i$ according to the tuth values $s(c'_i)$ and $s(c''_i)$ to make formulas $\psi$ and  $(c''_i\rightarrow w_i)$ to be true. There  must be some $w_i$ which is false. Then if we set $w$ to be false, $K$ is still be satisfied by $s$ (because clauses in $C_3$ are satisfied). This contradict the $V$-euivalence.\\

It must be that $C_3\subseteq K$, i.e., $w\rightarrow (c'_1\vee c_1'')\wedge\cdots\wedge (c'_n\vee c''_n)$ is in $K$. Suppose it is not the case. Similar as above, there would be a satisfying truth assigment of $K$ which makes some $w_i$ false, contradicts the $V$-equivalence. \\


Suppose $K\not\models c'_i$. Then $\psi\wedge\neg c'_i \wedge (c''_i\rightarrow w_i)$ must be in $K$. 
Otherwise, $K\cup\{\neg c'_i\}$ is consitent,  then there is a satisfying truth assignment $t$ for $K$ such that $t(c'_i)=0, t(w)=1, t(w_i)=0$. (In fact by our assumption, $t$ can be assumed to satisfiy $(c'_1\vee c''_1)\wedge\cdots\wedge (c'_n\vee c''_n)$ because every clause contains positive literal from $\vec{y}\cup\vec{z}$). This contradict the fact that $K\equiv_V\beta$.


Now we can see for each $i$, either $K\models \neg c'_i$ or $K\models c'_i$. 
That is, for any two satisfying truth assignments $t_1, t_2$ of $K$, each $c'_i$ has the same truth under $t_1\uparrow \vec{x}$ and $t_2\uparrow\vec{x}$.  \\





Now fix a trut assigment $e$ on $\vec{x}$ which can be extended to a satisfying truth assigment of $K$. 

Consider any truth assigment $s$ on $\vec{y}$. Since $s$ can be extended to satisfy $\beta$, it can be extended to a truth assigment $t$ which satisfies $K$. Please note we can assmue that $t\uparrow\vec{x}$ is $e$. 
Since $w$ and $w\rightarrow (c'_1\vee c''_1)\wedge\cdots\wedge (c'_n\vee c''_n)$ are in $K$. We can see $t$ satisfy $\varphi$. 

Consequently, for any truth assigment $s$ on $\vec{y}$, $e*s$ can be extended to a satisfying truth assigment of $\varphi$. Thus, $\Phi$ is true.


\ \\ 

{\color{red} From left to right.\color{black}


Suppose $\Phi=\exists\vec{x}\forall\vec{y}\exists\vec{z}\varphi$ is true. 

Let $e$ be a truth assignment on $\vec{x}$ such that $\forall\vec{y}\exists\vec{x}\varphi[x/e]$ is true


Let $$K_0:=\{\psi\wedge \neg c'_i\wedge (c''_i\rightarrow w_i)\mid e(c'_i)=0, i=1,\cdots,n\}$$

$$K_1:=\{c'_i\mid e(c'_i)=1, i=1,\cdots,n\}$$

$$K_2:=\{x_i\mid e(x_i)=1, i=1,\cdots, n\}\cup\{\neg x_i\mid e(x_i)=0, i=1,\cdots,n\}$$

$$K:=K_0\cup K_1\cup K_2\cup C_3\cup\{w\}$$


Consider any truth assignment $s$ on $V$. 

Suppose $s$ can be extended to satisfy $K$. Say the extenson is $t$. Since $w\in K$, $(c'_1\vee c''_1)\wedge\cdots\wedge(c'_n\vee c'_n)$ be be true under $t$. By formulas in $K_0$, we can see each $w_i$ is true under $t$. That means $s$ make $\beta$ true. Thus, $K\models_V\beta$. \\

Now suppose $s$ satisfies $\beta$. Since $\Phi$ is true, $e*(s\uparrow\vec{y})$ can  be extended to satisfy $\Phi$. Let $t$ be such an extension. Next we show $t$ can be extended to satisies $K$. Since $t$ makes $\varphi$ true, either $c'_i$ is true or $c''_i$ is true. We set each $w_i$ to be true. Then all clauses in $K_0$ are true. Set $w$ to be true. Then clauses in $C_3$ are true. Please note formulas in $K_1\cup K_2$ are already atisfied by $e$. Consequently, $s$ can be extended to satisfy $K$.
Hence, $\beta\models_V K$.\\

Altogether we obtain $K\equiv_V \beta$.








\ \ \\

{\bf Implication Problem}\\

Input: $C=\{\alpha_1,\cdots,\alpha_n\}$, $\beta$

Query: Whether $\exists K\subseteq C: K\models \beta$\\ 

Clearly in $\Sigma_2^P$. We shall the hardness

Consider $\Phi=\exists x_1,\cdots, x_n\forall y_1,\cdots,y_m \varphi$ where $\varphi$ is a DNF formula. Pick a new varibale $z$.

Let $C:=\{\varphi\rightarrow z, x_1,\neg x_1,\cdots, x_n,\neg x_n\}$, $\beta:=z$

Clearly, $\Phi$ is true if and only if $\exists K\subseteq C$ such that $K$ is satisfiable and $K\models \beta$.


\ \\ 

Note: In all problems $K$ is demanded satisfiable.

$$\alpha \equiv_V \beta \Longleftrightarrow \forall \gamma \mbox{ over } V, (\alpha\models \gamma \Leftrightarrow \beta\models \gamma) $$

$$\alpha \models_V \beta \Longleftrightarrow \forall \gamma \mbox{ over } V, (\beta\models \gamma \Longrightarrow \alpha\models \gamma) $$


%%%%%%%






%%%%%%%%%%%%%%%%%%%%%%%%%%%


\section{Resticted to DHORN}

$C$: set of DHORN, $\beta$: DHORN \\

{\bf Equivalence problem is in PTIME} \\

Idea: just checked IMP$(C,\beta)\equiv \beta$. 



%%%

\ \\

{\bf Implication problem is trivial} \\ 

The existence of $K$ is equivalent to $C\models\beta$\\

\ \\


{\bf The $V$-equivalence problem}\\

%IMP$(C,\beta,V):=\{\alpha\in C\mid \beta\models_V \alpha\}$\\

%The existence of $K\equiv_V \beta$ is equivalent to IMP$(C,\beta, V)\equiv_V\beta$.\\

we guess it seems $\Sigma_2^P$-complete.

See Hans's book page 251


\section{Restricted to HORN}


Equivalence Problem: same as the DHORN case (PTIME).\\

Desired $K$ exists iff IMP$(C,\beta)$ is satisfiable and IMP($C,\beta)\models \beta$\\ 

\ \\

V-Equivalence Configuration Problem :  $\Sigma_2^P$-complete\\ 


$$\Phi:=\exists y_1,\cdots, y_k \forall x_1,\cdots, x_m \left(c_1\vee\cdots\vee c_n \right)$$
%
Where $c_i$ is a conjunction of literals.\\

for each variable $z$, introduce a new variable $\pi(\neg z)$. Let $\pi(z)=z$.\\

introduce $U$.\\

Let $$\psi_0:=\left(\bigwedge_{j=1}^m (\neg \pi(\neg x_j)\vee \neg x_j)\right), \ \psi_1:= \left(\bigwedge_{i=1}^k(\neg \pi(\neg y_i)\vee \neg y_i)\right)$$

$$\theta:=\left(\bigvee_{i=1}^m (\neg x_i\wedge \neg\pi(\neg x_i))\right)$$

%$$\theta_i:=\left(\bigvee_{x\not\in c_i, \neg x\not\in c_i}(\neg x\wedge\neg\pi(\neg %x))\right)$$

Please note that $\theta$ is not HORN  when $n>1$. Forturnately, by using Tseiting algorithm, one can transform  $\theta$ to an equivalent HORN formula when restricted to old variables. \\  



For a conjunction $c=L_1\wedge\cdots\wedge L_s$, we write 
$\pi(c):=\pi(L_1)\wedge\cdots\wedge \pi(L_s)$


$$\begin{array}{lcl}C_0&:=&\{\psi_0\wedge\psi_1 \wedge\left( \bigwedge_{i=1}^n(\pi(c_i)\rightarrow U\vee \theta)\right)\}\\ 

C&:=&C_0\cup \{y_i,\pi(\neg y_i)\mid i=1,\cdots,k\}\\
\beta&:= &(U\vee\theta)\wedge \psi_0 \\
V&:=&\{U\}\cup\{x_1,\cdots,x_m,\pi(\neg x_1),\cdots, \pi(\neg x_m)\}
\end{array}$$

We shall show 

$$(\exists K\subseteq C \text{ such that } K\equiv_V \beta) \text{ if and only if $\Phi$ is true}.$$

\ \\

\color{red} 
!!!! I suddenly find that $U\vee \theta $ may not be HORN. Forturnately we can change $U$ to $\neg U$ in $C$ and $\beta$. Then the following proof should be changed accordingly 
\color{black}\\

Suppose $\Phi$ is true. There is truth assignment
$e$ on $\{y_1,\cdots, y_m\}$ such that $\forall x_1,\cdots,x_m\varphi[\vec{y}/e]$ is true, where $\vec{y}=y_1\cdots,y_k$. Define 
%
$$K=C_0\cup \{y_i\mid t(y_i)=1, 1\leq i\leq k\}\cup \{\pi(\neg y_i)\mid t(y_i)=0, 1\leq i\leq k\}$$

For any satisfying truth assignment $t$ for $K$, if it makes $\theta$ true then $\beta$ is true under $t$. Suppose $t$ makes $\theta$ false, then $t$ corresponds a truth assignment on $x_1,\cdots, x_n$ accoding the truth of $x_i$ and $\pi(\neg x_i)$. Since $\Phi$ is true, some  $\pi(c_i)$ must be true under $t$, then $T(U)=1$. Therefore, $t(\beta)=1$.

Suppose $s$ is a satisfying truth assignment for $\beta$. Then $s*e$ satisfies $\psi_0\wedge \psi_1$. If $s$ makes $\theta$ true, then $s*e$ satisfies $K$. Suppose $s(\theta)=0$. Then $s(U)=1$, hence $K$ is still satisfied by $s*e$. 

Altogether, we have $K\equiv_V\beta$.\\


For the inverse direction, suppose there is satisfiable $K\subseteq C$ such that $K\equiv_V\beta$. 


Clearly, the formula in $C_0$ must be in $K$. Then by formula $\psi_1$, either $y_i$ or  $\pi(\neg y_i)$ is not in $K$. 

Pick a truth assignment $e$ on $\{y_1,\cdots, y_k\}$ such that if $y_i\in K$ then $e(y_i)=1$, and $e(y_i)=0$  if else. 

We need to show $\forall x_1,\cdots,x_m(c_1\vee\cdots\vee c_n)$ is true.

Consider any truth assigment $s$ on $\{x_1,\cdots, x_m\}$. Let $s'$ be the assignment defined by $s'(\pi(\neg x_i)=1$ iff $s(x_i)=0$. Then $e'*s'$ satisfies $\psi_0\wedge\psi_1$, where $e'$ is obtained from $e$ is the same way as $s'$. 
We claim that, $(e'*s')$ makes $\pi(c_i)$ true for some $i$. Otherwise, we could set $U$ to be false,  and get a truth assignment satisfying $K$ but bot satisfying $\beta$ (please note that $s'(\theta)=0$), contradict the $V$-quivalence. 

Consequently, $\Phi$ is true.
 
\ \\

Implication Problem

NP-complete  

Given a 3CNF  $F$

$$\bigwedge_{i=1}^m (L_{i,1}\vee L_{i,2}\vee L_{i,3}) \ \mbox{ over } x_1,\cdots, x_n$$

For each $i=1,\cdots,m$, pick a new variable $z_i$. For each $j=1,\cdots, n$ we pick a new variable $\pi(\neg x_j)$. For convenience, we also write $x_j$ as $\pi(x_j)$. 

Define $C$ 

$$\begin{array}{ll}C:=&
\bigcup_{i=1}^m\{\pi(L_{i,1})\rightarrow z_i, \pi(L_{i,2})\rightarrow z_i, \pi(L_{i,3})\rightarrow z_i\}\cup\\ & \bigcup_{j=1}^n\{\rightarrow x_j, \rightarrow \pi(\neg x_j\} \cup\\ &
\{z_1\wedge\cdots\wedge z_m\rightarrow z\}\end{array}$$

Define 

$$\beta:=z\wedge\bigwedge (\neg \pi(\neg x_j)\vee \neg x_j)$$


Impliation problem iff $F$ is satisfiable \\


\ \\


Specification Problem\\

Given a partial configuration $K$, demand $\beta$, a set of variables $V,W$

Looking for $\sigma$ over $W$ such that

\begin{enumerate}
\item $K\wedge \sigma(W)\equiv \beta$

\item $K\wedge\sigma(W) \equiv_V\beta$

\item $K\wedge\sigma(W)\models \beta$
\end{enumerate}


Query Learning 

black box $\alpha$   

equivalence query. Guess a $\beta$ ask whether $\alpha\equiv \beta$. If the answer is no, output a truth assignment satisfying $\alpha$ and $\neg \beta$ or satisfying $\neg\alpha$ and $\beta$.\\

membership query

guess a truth assignment $v$ answer $v(\alpha)=0$ or 1. \\



%%%%%%%%%



 


\section{Configuration with constraints}

$C=\{\alpha_1,\cdots, \alpha_n\}, \beta$,
$D$ is set of formulas over $A_1,\cdots, A_n$ which are propositional atoms.
Whether there is $K\subseteq C$ such that 
\begin{itemize}
\item $K$ is satisfiable,
\item $K\equiv\beta$, and
\item the truth assignment $v_K$ satisfies $D$, where $v_K(A_i)=\left\{\begin{array}{ll}
1 & \text{if } \alpha_i\in K\\ 0 & \text{if }\alpha_i\not\in K\end{array}\right.$  

\end{itemize}

Duppose $D$, $\beta$ are DHORN, $D$ is 2HORN, then NP-complete.\\

%2HORN formula $H$, and $t$ is a conjunction of propositional atoms, $V$ a set variables with distint atoms from $t$.

%Determine whether there is a set $s\subseteq V$ such that $H$ is consistent and $s\wedge H\models t$. 

%This problem is NP-complete. 

Let $F$ be an arrbitrary 3CNF formula $c_1\wedge \cdots\wedge c_n$ with $c_i:=l_{i,1}\vee l_{i,2}\vee l_{i,3}$  over $\{x_1,\cdots, x_m\}$


pick new variable $\pi(\neg x_i)$ for $\neg x_i$. $\pi(x_i)$ is $x_i$. 

introduce new variables $w_1, \cdots, w_n$. Let

$$\begin{array}{l}H_0=\{\pi(l_{i,j})\rightarrow w_i\mid 1\leq i\leq n, j=1,2,3\}\\
D:=\{\neg x_1\vee \neg \pi(\neg x_1), \cdots, \neg x_m\vee \neg \pi(\neg x_m)\}\\
H:=H_0\cup D\end{array}$$, 

Let $\beta:=w_1\wedge\cdots\wedge w_n$. $V=\{x_1, \pi(\neg x_1),\cdots, x_m,\neg x_m\}$. 

Clearly $F$ is satisfiable iff there is $s\subseteq V$ such that $s\wedge H\models \beta$. \\


Next we transform $H$ to the constraint configuration problem for DHORN. 



For each literl $L$ over $\{x_1,\cdots, x_m\}$, define $$\alpha_i(\pi(L)):=\{w_j\mid \pi(L)\rightarrow w_j\in H_0\}$$

%For each $\pi(x_i)$, define $$\alpha_i^-=\{w_j\mid \pi(\neg x_i)\rightarrow w_j\}$$

Let $$K:=\{\alpha(\pi(L))\mid L\in\{x_1, \neg x_1,\cdots, x_m\neg x_m\}\}$$
%%
Now we can consider $\pi(L)$ the name of $\alpha(\pi(L))$. So, let 
$$D:=\{\neg x_1\vee \neg\pi(\neg x_1),\cdots, \neg x_m\vee\neg \pi(\neg x_m)\}$$

%
Clearly $K\equiv \beta$. 

Clearly, there is $s\subseteq V$ such that $v\wedge H\models \beta$ if and only if 

there is $s\subseteq V$ such that $s$ satisfies $D$ when $s$ is considered as a truth assigment and $\{\alpha(L)\mid L\in s\}\equiv \beta$.

Thus the constraint configuration problem for this case it NP-complete. \\



However, if $C:=\{\alpha_1,\cdots, \alpha_n\}, \beta$ and $D$ are all DHORN, then it is poly-time solvable. 

IMP$(C, \beta)$. Suppose it is satisfiable. (otherwsie retun no)

Please note that for any $\alpha\in C-\text{IMP}(C,\beta)$, $\alpha\wedge \text{IMP} \not\equiv \beta$


Let $D':=D\cup\{\neg A_i\mid \alpha_i\not\in\text{IMP}(C,\beta), \}$. 

If $D'$ is not satisfiable, then return no. 

Suppose $D'$ is sat. 

Check that IMP$(C,\beta)\equiv\beta$. if not return no. Suppose it is the case. 

Let IMP$_1:=\text{IMP}()-\{\alpha_i\mid D'\models \neg A_i\}$

Check that IMP$_1$ equivalent to $\beta$. If it is the case then return yes, return no else. 







\end{document}